RBE/CS549 Project: Boat Tracking/Detection

### 2017-12-14 paper/main.tex
Add section on cost function, remove unused proposal sections

@@

@@

\section{Evaluation Section from Proposal}

Because we do not have a labeled data set, we must develop
some way evaluate the performance of different algorithms.

In order to do this, we propose two general cost functions.
The first will evaluate the motion tracking features.
Essentially, when motion tracking, our objective is to
correctly predict the future path of an object. As such,
the cost function will assume a sane object detector and
use the difference between predicted frame-to-frame position
and actual frame-to-frame position (from the object detector)
as the cost.

For the object detector itself, a bit more complication is
required, and we hypothesize that the cost function will
consist of the following terms:

\begin{description}
\item[Object Deletion] Any unexpected object deletion shall
   be penalized, in order to avoid constantly losing track
   of objects between frames or over/under segmentation of
   individual objects. ``Expected'' object deletion would
   occur when an object that is already moving out of frame
   or behind another object disappears. In theory we also
   care about excessive object \emph{creation}; however,
   because the vast majority of created objects are also
   deleted eventually, the additional complication should
   be unnecessary. There is an open question about how
   to treat the deletion of objects that disappear over
   the horizon; however, such occurrences are hopefully
   rare enough or easily detectable enough that their
   cost should be insignificant (we don't want to
   accidentally \emph{not} penalize flickering objects
   that happen to fall on the horizon).
\item[Number of Objects] In order to avoid either a
   detector that never deletes objects or one that
   divides real objects into far too many individual
   objects, we shall penalize the number of objects
   identified in any given frame. This may be quadratic
   or some higher order function in order to avoid
   penalizing small numbers of objects excessively.
\item[Unaccounted for Area] To avoid an object
   detector that simply never returns any objects,
   we shall compare the area accounted for by the
   identified objects and the area that ``should''
   contain objects (per some naive estimate), and
   penalize any unaccounted for area.
   As an initial method for identifying this area,
   we propose that we (a) develop some simple detector
   for identifying sea water (it's mostly blue...),
   and (b) make a simple assumption about the location
   of the horizon (the existing video is relatively stable,
   so the horizon should be, and this way we won't have
   to worry about the sky). Any area below the estimated
   horizon that is not sea water ``should'' be part of
   an object (this includes the shore).
\end{description}

Obviously, the above cost function will not provide a perfect
measure of algorithm performance. However, between it and
qualitative sanity checks, we should be able to provide
a good estimate of the performance of our algorithms.

\section{Responsibilities Section from Proposal}
\begin{description}
\item[James Kuszmaul] Work on basic object detection and how
  to retain object associations between frames/measure .

\item[Jordan Burklund] Develop methods to segment and mask pixels that represent water. Explore methods using contours for object detection.
\end{description}

>>>>

\tableofcontents

@@

While we did not end up making much use of it, we did attempt to write a cost
function that would offer more objective evaluations of our algorithms (as we do
not have labeled data to perform some simple check against). The
motivation for this was both to (a) be able to run our algorithms over larger
segments of data without manually scoring it and (b) help us to better
understand our own priorities when writing our detection algorithms.

The cost function ultimately consisted of:

\begin{itemize}
\item A term penalizing the current number of objects (to avoid bloating the
      number of objects)
\item A term penalizing deletion of objects (to encourage correct association
      of objects between frames)
\item Penalty for inconsistency between actual changes in position (over
      multi-frame time periods, to avoid noise from single-frame disturbances)
      and the reported velocity
\item Penalty for substantial changes in bounding box dimensions (generally,
      objects stay roughly the same size over time)
\item Penalty for the amount of area not covered by objects that isn't blue,
      on the basis that most non-blue things are objects
\end{itemize}

This did appear to give some meaningful numbers, as when we incorporated
the HSV water segmentation in with the optical flow algorithm we saw a
substantial
improvement in cost (e.g., whereas the cost had been in the range of 125-135
when tweaking parameters with just optical flow, it cut down to 115 when the
water segmentation was added). However, we made limited use of the raw
cost number beyond this.

@@
